---
title: "IV Example"
output:
  html_document:
    df_print: paged
  html_notebook: default
  pdf_document: default
---

来源: https://bookdown.org/ccolonescu/RPoE4/random-regressors.html

```{r message=F}
library(AER) #for `ivreg()`
library(lmtest) #for `coeftest()` and `bptest()`.
library(broom) #for `glance(`) and `tidy()`
library(PoEdata) #for PoE4 datasets
library(car) #for `hccm()` robust standard errors
library(sandwich)
library(knitr) #for making neat tables with `kable()`
library(stargazer) 
library(sjPlot)
library(sjmisc)
library(plm)
library(sjlabelled)
```

# 模型

$$\begin{equation}
log(wage)=\beta_{1}+\beta_{2}educ+\beta_{3}exper+\beta_{4}exper^2+e
\label{eq:wagelm10}
\end{equation}$$

# 数据与第一阶段回归

$$\begin{equation}
educ=\gamma_{1}+\gamma_{2}exper+\gamma_{3}exper^2+\theta_{1}mothereduc+\nu_{educ}
\label{eq:firstStageEduc10}
\end{equation}$$

```{r}
data("mroz", package="PoEdata")
mroz1 <- mroz[mroz$lfp==1,] #restricts sample to lfp=1
educ.ols <- lm(educ~exper+I(exper^2)+mothereduc, data=mroz1)
kable(tidy(educ.ols), digits=4, align='c',caption=
  "First stage in the 2SLS model for the 'wage' equation")
```

# 第二阶段回归

```{r}
educHat <- fitted(educ.ols)
wage.2sls <- lm(log(wage)~educHat+exper+I(exper^2), data=mroz1)
kable(tidy(wage.2sls), digits=4, align='c',caption=
  "Second stage in the 2SLS model for the 'wage' equation")
```


# 修正标准误估计
```{r results='asis'}
data("mroz", package="PoEdata")
mroz1 <- mroz[mroz$lfp==1,] #restricts sample to lfp=1.
mroz1.ols <- lm(log(wage)~educ+exper+I(exper^2), data=mroz1)
mroz1.iv <- ivreg(log(wage)~educ+exper+I(exper^2)|
            exper+I(exper^2)+mothereduc, data=mroz1)
mroz1.iv1 <- ivreg(log(wage)~educ+exper+I(exper^2)|
            exper+I(exper^2)+mothereduc+fathereduc,
            data=mroz1)
tab_model(mroz1.ols, wage.2sls, mroz1.iv, mroz1.iv1,
		  emph.p = T, robust = T,
          show.ci = F, collapse.se = T, string.pred = "Coeffcient", show.se = F, 
		  dv.labels = c("OLS", "explicit 2SLS", "IV1", "IV2"),
          p.style = "a")
```


# 弱工具变量检验

$$\begin{equation}
educ=\gamma_{1}+\gamma_{2}exper+\gamma_{3} exper^2+\theta_{1} mothereduc+ \theta_{2}fathereduc+\nu
\label{eq:educlm10}
\end{equation}$$


```{r}
educ.ols <- lm(educ~exper+I(exper^2)+mothereduc+fathereduc, 
               data=mroz1)
tab <- tidy(educ.ols)
kable(tab, digits=4,
      caption="The 'educ' first-stage equation")
```

```{r}
linearHypothesis(educ.ols, c("mothereduc=0", "fathereduc=0"))
```

# specification tests

1. 内生性检验 (Hausman test for endogeneity)：$H_{0}:\;Cov(x,e)=0$

2. 过度识别检验：(overidentifying restrictions, or the Sargan test): $H_{0}:Cov(z,e)=0$

```{r}
summary(mroz1.iv1, diagnostics=TRUE)
```

检验的主要结论：

- Weak instruments test: rejects the null, meaning that at least one instrument is strong

- (Wu-)Hausman test for endogeneity: barely rejects the null that the variable of concern is uncorrelated with the error term, indicating that  educ  is marginally endogenous

- Sargan overidentifying restrictions: does not reject the null, meaning that the extra instruments are valid (are uncorrelated with the error term).
