---
title: "RNN in R"
output:
  html_document:
    df_print: paged
---


```{r message=F}
library(tidyverse)
library(glue)
library(forcats)

# Time Series
library(timetk)
library(tidyquant)
library(tibbletime)

# Visualization
library(cowplot)

# Preprocessing
library(recipes)

# Sampling / Accuracy
library(rsample)
library(yardstick) 

# Modeling
library(keras)
library(tfruns)
```

参考资料：
https://blogs.rstudio.com/ai/posts/2018-06-25-sunspots-lstm/

# 数据
```{r}
sun_spots <- datasets::sunspot.month %>%
    tk_tbl() %>%
    mutate(index = as_date(index)) %>%
    as_tbl_time(index = index)

sun_spots
```

# EDA

## Cowplot

```{r}
p1 <- sun_spots %>%
    ggplot(aes(index, value)) +
    geom_point(color = palette_light()[[1]], alpha = 0.5) +
    theme_tq() +
    labs(
        title = "From 1749 to 2013 (Full Data Set)"
    )

p2 <- sun_spots %>%
    filter_time("start" ~ "1800") %>%
    ggplot(aes(index, value)) +
    geom_line(color = palette_light()[[1]], alpha = 0.5) +
    geom_point(color = palette_light()[[1]]) +
    geom_smooth(method = "loess", span = 0.2, se = FALSE) +
    theme_tq() +
    labs(
        title = "1749 to 1759 (Zoomed In To Show Changes over the Year)",
        caption = "datasets::sunspot.month"
    )

p_title <- ggdraw() + 
  draw_label("Sunspots", size = 18, fontface = "bold", 
             colour = palette_light()[[1]])

plot_grid(p_title, p1, p2, ncol = 1, rel_heights = c(0.1, 1, 1))
```

# Backtesting:  

## 回溯策略

- training: 100 years (initial = 12*10 samples)
- testing: 50 years (assess = 12 * 50)
- skip: 22 years (skip = 12*22-1) 将样本大概均分为6部分覆盖整个265年的区间。
- cumulative = FALSE

```{r}
periods_train <- 12 * 100
periods_test  <- 12 * 50
skip_span     <- 12 * 22 - 1
rolling_origin_resamples <- rolling_origin(
  sun_spots,
  initial    = periods_train,
  assess     = periods_test,
  cumulative = FALSE,
  skip       = skip_span
)

rolling_origin_resamples
```
## 回溯策略可视化
```{r}
# Plotting function for a single split
plot_split <- function(split, expand_y_axis = TRUE, 
                       alpha = 1, size = 1, base_size = 14) {
    
    # Manipulate data
    train_tbl <- training(split) %>%
        add_column(key = "training") 
    
    test_tbl  <- testing(split) %>%
        add_column(key = "testing") 
    
    data_manipulated <- bind_rows(train_tbl, test_tbl) %>%
        as_tbl_time(index = index) %>%
        mutate(key = fct_relevel(key, "training", "testing"))
        
    # Collect attributes
    train_time_summary <- train_tbl %>%
        tk_index() %>%
        tk_get_timeseries_summary()
    
    test_time_summary <- test_tbl %>%
        tk_index() %>%
        tk_get_timeseries_summary()
    
    # Visualize
    g <- data_manipulated %>%
        ggplot(aes(x = index, y = value, color = key)) +
        geom_line(size = size, alpha = alpha) +
        theme_tq(base_size = base_size) +
        scale_color_tq() +
        labs(
          title    = glue("Split: {split$id}"),
          subtitle = glue("{train_time_summary$start} to ", 
                          "{test_time_summary$end}"),
            y = "", x = ""
        ) +
        theme(legend.position = "none") 
    
    if (expand_y_axis) {
        
        sun_spots_time_summary <- sun_spots %>% 
            tk_index() %>% 
            tk_get_timeseries_summary()
        
        g <- g +
            scale_x_date(limits = c(sun_spots_time_summary$start, 
                                    sun_spots_time_summary$end))
    }
    
    g
}
```

```{r}
rolling_origin_resamples$splits[[1]] %>%
    plot_split(expand_y_axis = TRUE) +
    theme(legend.position = "bottom")
```

```{r}
# Plotting function that scales to all splits 
plot_sampling_plan <- function(sampling_tbl, expand_y_axis = TRUE, 
                               ncol = 3, alpha = 1, size = 1, base_size = 14, 
                               title = "Sampling Plan") {
    
    # Map plot_split() to sampling_tbl
    sampling_tbl_with_plots <- sampling_tbl %>%
        mutate(gg_plots = map(splits, plot_split, 
                              expand_y_axis = expand_y_axis,
                              alpha = alpha, base_size = base_size))
    
    # Make plots with cowplot
    plot_list <- sampling_tbl_with_plots$gg_plots 
    
    p_temp <- plot_list[[1]] + theme(legend.position = "bottom")
    legend <- get_legend(p_temp)
    
    p_body  <- plot_grid(plotlist = plot_list, ncol = ncol)
    
    p_title <- ggdraw() + 
        draw_label(title, size = 14, fontface = "bold", 
                   colour = palette_light()[[1]])
    
    g <- plot_grid(p_title, p_body, legend, ncol = 1, 
                   rel_heights = c(0.05, 1, 0.05))
    
    g
    
}
```

```{r}
rolling_origin_resamples %>%
    plot_sampling_plan(expand_y_axis = T, ncol = 3, alpha = 1, size = 1, base_size = 10, 
                       title = "Backtesting Strategy: Rolling Origin Sampling Plan")
```



设定`expand_y_axis = FALSE`放大到样本区间：

```{r}
rolling_origin_resamples %>%
    plot_sampling_plan(expand_y_axis = T, ncol = 3, alpha = 1, size = 1, base_size = 10, 
                       title = "Backtesting Strategy: Rolling Origin Sampling Plan")
```

# LSTM 模型

```{r}
example_split    <- rolling_origin_resamples$splits[[6]]
example_split_id <- rolling_origin_resamples$id[[6]]
plot_split(example_split, expand_y_axis = FALSE, size = 0.5) +
    theme(legend.position = "bottom") +
    ggtitle(glue("Split: {example_split_id}"))
```

## 数据准备
```{r}
df_trn <- analysis(example_split)[1:800, , drop = FALSE]
df_val <- analysis(example_split)[801:1200, , drop = FALSE]
df_tst <- assessment(example_split)
```
```{r}
df <- bind_rows(
  df_trn %>% add_column(key = "training"),
  df_val %>% add_column(key = "validation"),
  df_tst %>% add_column(key = "testing")
) %>%
  as_tbl_time(index = index)

df
```

## 用recipes进行预处理

LSTM的输入数据最好是经过标准化之后的。我们先对数据做变换处理。
```{r}
rec_obj <- recipe(value ~ ., df) %>%
    step_sqrt(value) %>%
    step_center(value) %>%
    step_scale(value) %>%
    prep()
df_processed_tbl <- bake(rec_obj, df)
df_processed_tbl
```

记住变换历史以便back-transform

```{r}
center_history <- rec_obj$steps[[2]]$means["value"]
scale_history  <- rec_obj$steps[[3]]$sds["value"]

c("center" = center_history, "scale" = scale_history)
```

## reshape 数据

Keras LSTM 要求输入和输出数据满足一定的格式要求。输入数据必须是一个3-d array包括

1. num_samples：观测数量

2. num_timestep：隐藏层的长度

3. num_features：单变量时间序列则为1


```{r}
n_timesteps <- 12
n_predictions <- n_timesteps
batch_size <- 10

# functions used
build_matrix <- function(tseries, overall_timesteps) {
  t(sapply(1:(length(tseries) - overall_timesteps + 1), function(x) 
    tseries[x:(x + overall_timesteps - 1)]))
}

reshape_X_3d <- function(X) {
  dim(X) <- c(dim(X)[1], dim(X)[2], 1)
  X
}

train_vals <- df_processed_tbl %>%
  filter(key == "training") %>%
  select(value) %>%
  pull()
valid_vals <- df_processed_tbl %>%
  filter(key == "validation") %>%
  select(value) %>%
  pull()
test_vals <- df_processed_tbl %>%
  filter(key == "testing") %>%
  select(value) %>%
  pull()

# build the windowed matrices
train_matrix <-
  build_matrix(train_vals, n_timesteps + n_predictions)
valid_matrix <-
  build_matrix(valid_vals, n_timesteps + n_predictions)
test_matrix <- build_matrix(test_vals, n_timesteps + n_predictions)

# separate matrices into training and testing parts
# also, discard last batch if there are fewer than batch_size samples
# (a purely technical requirement)
X_train <- train_matrix[, 1:n_timesteps]
y_train <- train_matrix[, (n_timesteps + 1):(n_timesteps * 2)]
X_train <- X_train[1:(nrow(X_train) %/% batch_size * batch_size), ]
y_train <- y_train[1:(nrow(y_train) %/% batch_size * batch_size), ]

X_valid <- valid_matrix[, 1:n_timesteps]
y_valid <- valid_matrix[, (n_timesteps + 1):(n_timesteps * 2)]
X_valid <- X_valid[1:(nrow(X_valid) %/% batch_size * batch_size), ]
y_valid <- y_valid[1:(nrow(y_valid) %/% batch_size * batch_size), ]

X_test <- test_matrix[, 1:n_timesteps]
y_test <- test_matrix[, (n_timesteps + 1):(n_timesteps * 2)]
X_test <- X_test[1:(nrow(X_test) %/% batch_size * batch_size), ]
y_test <- y_test[1:(nrow(y_test) %/% batch_size * batch_size), ]
# add on the required third axis
X_train <- reshape_X_3d(X_train)
X_valid <- reshape_X_3d(X_valid)
X_test <- reshape_X_3d(X_test)

y_train <- reshape_X_3d(y_train)
y_valid <- reshape_X_3d(y_valid)
y_test <- reshape_X_3d(y_test)
```


## 建立LSTM 模型

```{r}
FLAGS <- flags(
  # There is a so-called "stateful LSTM" in Keras. While LSTM is stateful
  # per se, this adds a further tweak where the hidden states get 
  # initialized with values from the item at same position in the previous
  # batch. This is helpful just under specific circumstances, or if you want
  # to create an "infinite stream" of states, in which case you'd use 1 as 
  # the batch size. Below, we show how the code would have to be changed to
  # use this, but it won't be further discussed here.
  flag_boolean("stateful", FALSE),
  # Should we use several layers of LSTM?
  # Again, just included for completeness, it did not yield any superior 
  # performance on this task.
  # This will actually stack exactly one additional layer of LSTM units.
  flag_boolean("stack_layers", FALSE),
  # number of samples fed to the model in one go
  flag_integer("batch_size", 10),
  # size of the hidden state, equals size of predictions
  flag_integer("n_timesteps", 12),
  # how many epochs to train for
  flag_integer("n_epochs", 100),
  # fraction of the units to drop for the linear transformation of the inputs
  flag_numeric("dropout", 0.2),
  # fraction of the units to drop for the linear transformation of the 
  # recurrent state
  flag_numeric("recurrent_dropout", 0.2),
  # loss function. Found to work better for this specific case than mean
  # squared error
  flag_string("loss", "logcosh"),
  # optimizer = stochastic gradient descent. Seemed to work better than adam 
  # or rmsprop here (as indicated by limited testing)
  flag_string("optimizer_type", "sgd"),
  # size of the LSTM layer
  flag_integer("n_units", 128),
  # learning rate
  flag_numeric("lr", 0.003),
  # momentum, an additional parameter to the SGD optimizer
  flag_numeric("momentum", 0.9),
  # parameter to the early stopping callback
  flag_integer("patience", 10)
)

# the number of predictions we'll make equals the length of the hidden state
n_predictions <- FLAGS$n_timesteps
# how many features = predictors we have
n_features <- 1
# just in case we wanted to try different optimizers, we could add here
optimizer <- switch(FLAGS$optimizer_type,
                    sgd = optimizer_sgd(lr = FLAGS$lr, 
                                        momentum = FLAGS$momentum)
                    )

# callbacks to be passed to the fit() function
# We just use one here: we may stop before n_epochs if the loss on the
# validation set does not decrease (by a configurable amount, over a 
# configurable time)
callbacks <- list(
  callback_early_stopping(patience = FLAGS$patience)
)
```

建模

```{r}
model <- keras_model_sequential()

model %>%
  layer_lstm(
    units = FLAGS$n_units,
    batch_input_shape = c(FLAGS$batch_size, FLAGS$n_timesteps, n_features),
    dropout = FLAGS$dropout,
    recurrent_dropout = FLAGS$recurrent_dropout,
    return_sequences = TRUE,
    stateful = FLAGS$stateful
  )

if (FLAGS$stack_layers) {
  model %>%
    layer_lstm(
      units = FLAGS$n_units,
      dropout = FLAGS$dropout,
      recurrent_dropout = FLAGS$recurrent_dropout,
      return_sequences = TRUE,
      stateful = FLAGS$stateful
    )
}
model %>% time_distributed(layer_dense(units = 1))

model %>%
  compile(
    loss = FLAGS$loss,
    optimizer = optimizer,
    metrics = list("mean_squared_error")
  )

if (!FLAGS$stateful) {
  model %>% fit(
    x          = X_train,
    y          = y_train,
    validation_data = list(X_valid, y_valid),
    batch_size = FLAGS$batch_size,
    epochs     = FLAGS$n_epochs,
    callbacks = callbacks
  )
  
} else {
  for (i in 1:FLAGS$n_epochs) {
    model %>% fit(
      x          = X_train,
      y          = y_train,
      validation_data = list(X_valid, y_valid),
      callbacks = callbacks,
      batch_size = FLAGS$batch_size,
      epochs     = 1,
      shuffle    = FALSE
    )
    model %>% reset_states()
  }
}

if (FLAGS$stateful)
  model %>% reset_states()
```

```{r}
pred_train <- model %>%
  predict(X_train, batch_size = FLAGS$batch_size) %>%
  .[, , 1]

# Retransform values to original scale
pred_train <- (pred_train * scale_history + center_history) ^2
compare_train <- df %>% filter(key == "training")

# build a dataframe that has both actual and predicted values
for (i in 1:nrow(pred_train)) {
  varname <- paste0("pred_train", i)
  compare_train <-
    mutate(compare_train,!!varname := c(
      rep(NA, FLAGS$n_timesteps + i - 1),
      pred_train[i,],
      rep(NA, nrow(compare_train) - FLAGS$n_timesteps * 2 - i + 1)
    ))
}
```

```{r}
coln <- colnames(compare_train)[4:ncol(compare_train)]
cols <- map(coln, quo(sym(.)))
rsme_train <-
  map_dbl(cols, function(col)
    rmse(
      compare_train,
      truth = value,
      estimate = !!col,
      na.rm = TRUE
    )) %>% mean()

rsme_train
```





coln <- colnames(compare_train)[4:ncol(compare_train)]
cols <- map(coln, quo(sym(.)))
rsme_train <-
  map_dbl(cols, function(col)
    rmse(
      compare_train,
      truth = value,
      estimate = !!col,
      na.rm = TRUE
    )) %>% mean()

rsme_train

















